Estimating duration in the presence of misclassification

### 2024-02-08 ATACCC.tex
add posterior probability that ATACCC shorter

The $F_{D,g}$ estimates for the two groups are in \cref{ATACCC:fig:duration}.
The vaccinated population have shorter durations of RT-PCR positivity\todo{check posterior probability that vaccinated population have shorter durations} than the unvaccinated population (see \cref{ATACCC:fig:duration}).
The median duration of RT-PCR positivity for the vaccinated population is 13 days (95\% CrI: 11--16 days), but it is 16 days (95\% CrI: 14--19 days) for the unvaccinated population.
\begin{figure}
  \centering \includegraphics{ATACCC/duration}
  \caption[Duration of RT-PCR positivity.]{Estimated distribution (survival function) of duration of RT-PCR positivity for the two populations. The vaccinated population have shorter durations of RT-PCR positivity.  \label{ATACCC:fig:duration}}
\end{figure}

>>>>

The $F_{D,g}$ estimates for the two groups are in \cref{ATACCC:fig:duration}.
The vaccinated population very likely has a shorter duration of RT-PCR positive (93\% posterior probability of a shorter median duration) than the unvaccinated population (see \cref{ATACCC:fig:duration}).
The median duration of RT-PCR positivity for the vaccinated population is 13 days (95\% CrI: 11--16 days), but it is 16 days (95\% CrI: 14--19 days) for the unvaccinated population.
\begin{figure}
  \centering \includegraphics{ATACCC/duration}
  \caption[Duration of RT-PCR positivity.]{Estimated distribution (survival function) of duration of RT-PCR positivity for the two populations. The vaccinated population have shorter durations of RT-PCR positivity.  \label{ATACCC:fig:duration}}
\end{figure}
